%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Skills}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvskills}

%------------------------------------------------

\cvskill
{Programming} % Category
{C++, C, Python, Javascript ,Java, C\#, VHDL, Javascript, PLpgSQL, SQL, UML, CSS, LaTex } % Skills

\hline
%------------------------------------------------

\cvskill
{Framework} % Category
{Qt, React, GWT(Google Web Toolkit), Hibernate, Unity3d} % Skills

%------------------------------------------------
\hline

\cvskill
{Development IDE} % Category
{Qt Creator, JetBrains Package, Eclipse, NetBeans ,Android Studio, Ada Multi} % Skills

\hline

%------------------------------------------------

\cvskill
{DMBS} % Category
{MySql, Postgres with PostGis plugin} % Skills

\hline
%------------------------------------------------

\cvskill
{Networking} % Category
{Managing and Maintaining the Servers, PC's, Routers and Switches.
	Configuring, Managing and Maintaining \newline Networking Equipments,
	Installing, configuring and \newline administering network technologies 
} % Skills
\hline
\cvskill
{Embedded System} % Category
{Micro-controller programming: ESP32, ARM, Arduino Based.  \newline
 FPGA programming: VHDL with experience of Xilinx software.
 Architectures on custom boards with multiple microcontrollers. 
 Development of custom carrier board. Use of multiple sensors breakout-board
} % Skill
\hline
%------------------------------------------------
\cvskill
{Methodology} % Category
{Excellent Knowledge in Software Engineering and Design(GOF Pattern), Agile methodology, RUP, SCRUM. \newline User-centered design (UCD).
 Advanced use of UML with profiling. Queueing theory applied to software \newline performance. In-depth knowledge of the main architectural patterns: MVC, MVP, Client-server, \newline Layered.
} % Skill

\hline
\cvskill
{Other} % Category
{Electronic warfare systems, Principles of space SW Engineering, Principles of responsive web design
} % Skill

\hline
\cvskill
{Certification} % Category
{Qt And QML Essentials, Cisco CCNA Routing and Switching certification Part 1} % Skills
\hline
\cvskill
{Languages} % Category
{Italian, English} % Skills

%------------------------------------------------

\end{cvskills}